Visit Scotland Analysis

### 2023-06-19 visit_scotland_analysis.Rmd
Added Diagnostic Tests for Linear Model / Removed Unused Data from Cleaning Script

```{r}
library(tidyverse)
library(here)
library(sf)
library(infer)
library(ggridges)
library(modelr)
library(skimr)
```

@@

regional_domestic_tourism_all <- read_csv(here("data/clean_data/regional_domestic_tourism_all_clean.csv"))
regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
regional_domestic_tourism_non_gb_clean <- read_csv(here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
tourism_businesses <- read_csv(here("data/clean_data/tourism_businesses_clean.csv"))
dom_int_summary <- read_csv(here("data/clean_data/dom_int_summary_clean.csv"))
# international_visits_annual_summary <- read_csv(here("data/clean_data/international_visits_annual_summary_clean.csv"))
# domestic_annual <- read_csv(here("data/clean_data/domestic_annual_clean.csv"))

@@

##### Linear Model: Predict Spend by Visits & Nights?

@@

```{r}
regional_domestic_tourism_non_gb_clean %>% 
  filter(local_authority == "City of Edinburgh",
         region_of_residence == "England") %>% 
  summarise(cor(expenditure, nights))
```

@@

>>>>

```{r}
library(tidyverse)
library(here)
library(sf)
library(infer)
library(ggridges)
library(modelr)
library(skimr)
library(ggfortify)
```

@@

regional_domestic_tourism_individual <- read_csv(here("data/clean_data/regional_domestic_tourism_individual_clean.csv"))
regional_domestic_tourism_non_gb_clean <- read_csv(here("data/clean_data/regional_domestic_tourism_non_gb_clean.csv"))
international_visits <- read_csv(here("data/clean_data/international_visits_clean.csv"))
tourism_businesses <- read_csv(here("data/clean_data/tourism_businesses_clean.csv"))
dom_int_summary <- read_csv(here("data/clean_data/dom_int_summary_clean.csv"))

@@

##### Linear Model: Predict Spend by Visits

@@

@@

```{r}
autoplot(model_edinburgh)
```

- Residuals vs. Fitted (Tests Independence of Residuals): No strong evidence of a pattern. 
- Normal Q-Q (Tests Normality of Residuals): Distribution of standardised residuals appears fairly normal. 
- Scale-Location (Tests Constancy of Variation of Residuals): No strong evidence of funneling.
